% Proposed amendments to the
% TECH SQUARES CONSTITUTION and BYLAWS
\documentstyle[11pt,conmac]{article}
\amendment
\title{Amendments to Tech Squares Constitution and Bylaws}
\pagefooter{Proposed Amendments}{-- \thepage\ --}{7 Jun 94}
\begin{document}
\maketitle
\begin{history}
Proposed 7 Jun 1994
\end{history}

Constitution


\nextchange
In Article II, Membership, change Section 3 as follows:

\current Any club member who \del{attends club dances and/or other
club activities frequently shall be a
{\it voting member.\/}
The Bylaws shall specify attendance requirements for voting membership.}

\revised Any club member who \add{meets the attendance requirements specified in
the Bylaws shall be a {\it voting member.\/}}


\nextchange
In Article IV, Officers, change Section 2 as follows:

\current \del{The term of the elected officers shall be one year.}

\revised \add{The term for officers elected in the spring shall be seven
months, with an option to continue in office for an additional five
months without re-election.  Officers elected in the fall, if any,
shall hold office for five months.}


\nextchange
In Article V, The Executive Committee, change Section 2 as follows:

\current The \del{members of the} Executive Committee shall be
the elected \del{and appointed club} officers \del{and the Members-at-Large.}
Executive Committee members are encouraged to attend Executive
Committee meetings.

\revised The Executive Committee shall be \add{comprised of the five} elected
officers.  Executive Committee members are encouraged to attend Executive
Committee meetings.


\nextchange
In Article V, The Executive Committee, change Section 5 as follows:

\current Each elected officer shall have one vote on the Executive Committee.
\del{Appointed officers do not have a vote.}

\revised Each elected officer shall have one vote on the Executive Committee.


\nextchange
In Article VIII, Club Employees, change Section 4 as follows:

\current No person may be a club officer and a club employee concurrently.

\revised No person may be \add{an elected} club officer and a club employee concurrently.


\nextchange
In Article XI, Ratification, add an apostrophe in Section 1 as follows:

\revised \ldots four weeks\add{'} notice \ldots


\vskip .25in

Bylaws


\nextchange
In Article I, Membership, change Section 1 as follows:

\current A person who did not go through the class must attend \del{70% of the total
number of club and monthly dances during a three}-month period to become
a member of the club.

\revised A person who did not go through the class must \add{have attended at
least five club or monthly dances in a four}-month period to become
a member of the club.


\nextchange
In Article I, Membership, change Section 2 as follows:

\current Voting members shall have attended at least five club \del{and/}or monthly
dances in the last four months, \ldots.

\revised Voting members shall have attended at least five club or monthly
dances in the last four months, \ldots.


\nextchange
In Article II, Officers and Their General Duties, change Section 2 as follows:

\current \del{Officers} shall attend \del{all} Executive Committee meetings.

\revised \add{Executive Committee members} shall attend Executive
Committee meetings.


\nextchange
In Article III, Officers' Specific Duties, change Section 5, second
duty as follows:

\current take admission \del{for} class members

\revised take admission \add{from} class members


\nextchange
In Article IV, The Executive Committee, add an apostrophe in Section 3 as follows:

\revised \ldots twenty-four hours\add{'} notice \ldots


\nextchange
In Article V, Meetings, add an apostrophe in Section 3 as follows:

\revised \ldots two weeks\add{'} notice \ldots


\nextchange
In Article VIII, The Class, change Section 1 as follows:

\current Except at the discretion of the Executive Committee, the class shall
be \del{12} weeks, preceded by at most two free nights.

\revised  Except at the discretion of the Executive Committee, the class shall
be \add{14} weeks, preceded by at most two free nights.


\nextchange
In Article IX, Elections, change Section 1 as follows:

\current \del{Annual election of the club officers shall be held as close as
practical to the first week of March.  The elected officers shall
assume their duties at the first club activity in May.}  A majority of
the votes cast by the voting members present shall be required to elect any of the officers.

\revised \add{The term of office for officers elected in the spring shall begin on the earlier
of one week after the spring class graduation or June 1.  The term of
office for officers elected in the fall, if any, shall begin on the earlier of one week
after the fall class graduation or January 1.  Elections shall be
held as close as is
practical to two months prior to the inception of office.  Fall
elections, if any, shall be held only for the positions vacated by
elected officers who have chosen not to continue in office.}  A majority of
the votes cast by the voting members present shall be required to elect any of the officers.




\nextchange
In Article XI, Ratification, add an apostrophe in Section 1 as follows:

\revised \ldots four weeks\add{'} notice \ldots

\end{document}
