% Tech Squares Bylaws
% Ratified by a vote of 63 to 13
\documentclass{bylaws}
\title{Tech Squares Bylaws}
\date{16 Aug 94}
\begin{document}

\maketitle

\begin{history}
Adopted 22 May 1984
Amended 19 January 1988
Amended 1 March 1988
Amended 16 August 1994
\end{history}


\article{Membership}
\section
A person who did not go through the class must 
have attended at
least five club or monthly dances in a four-month period to become
a member of the club.
\section
Voting members shall have attended at least five club or monthly
dances in the last four months, except that non-attendance during
June, July, and August shall not be counted against a person.
\section
Club membership does not expire, though a club member may relinquish membership.

\article{Officers and Their General Duties}
\section
Club dances shall be run by elected officers,
appointed officers, committee members and interested club members.  A
schedule assigning duties to these people will be published in advance.
One of the assignments will be a Dance Supervisor, who will have
overall responsibility for the dance.  Other duties are
\duty
to open the hall before dances
\duty
to assist the caller and cuer at dances, including ensuring them help
to and from the hall
\duty
to ensure that members bring refreshments, coordinate the refreshments
to be brought, and set up the refreshments at appropriate club
functions
\duty		
to see that admission for non-class people is taken at club dances,
and keep a record of attendance at dances and submit it to the
Secretary
\duty		
to see that admission for class members is taken during the class and
keep a record of attendance and submit it to the Secretary
\duty
pay the caller and cuer by the end of each club and monthly dance
\duty		
ensure that the hall is closed properly after dances

\section
Executive Committee members shall attend Executive Committee meetings.
\section
An officer's vote on the Executive Committee may be transferred
only by written proxy.
\section
Officers shall train and advise their successor.
\section
Committee chairs shall appoint assistants to their committees.  Four
assistants are recommended.  The committees members are appointed
subject to the approval of the Executive Committee.  Committee members
shall serve for one year at the discretion of the Executive Committee
except for Class Assistants.  Class Assistants shall serve from six
weeks before the start of a class until class graduation.

\article{Officers' Specific Duties}
\section
The President shall
\duty
call and chair meetings of the club and the Executive Committee
\duty
be a member of all committees
\duty
appoint temporary officers as necessary
\duty
review the club's contracts with the club caller and the club cuer each year
\duty
make announcements at dances
\duty
schedule and coordinate people for dance duties.

\section
The Treasurer shall
\duty
receive and pay all monies of the club as authorized by it
\duty
be directly responsible for its financial transactions
\duty
handle all financial records, keeping them orderly, accurate, and up-to-date
\duty
report at each club meeting on the financial status of the club
\duty
report to the President.

\section
The Secretary shall
\duty
maintain up-to-date written minutes of club and Executive Committee
meetings
\duty
maintain a list of club members, and their voting status
\duty
handle club correspondence, except as otherwise governed by the
Constitution or Bylaws
\duty
each year review the copy of the Constitution on file with
the Association of Student Activities (ASA) and ensure that it
is up-to-date
\duty
inform the ASA of the names of all persons elected as officers of the
club within one month of their election
\duty
inform the ASA of any changes in the club Constitution within one
month of their adoption
\duty
attend ASA meetings as appropriate
\duty
report to the President.

\section
The Publicity Coordinator shall report to the President.  The
Publicity Assistants shall report to the Publicity Coordinator.
The Publicity Coordinator and Publicity
Assistants shall organize club and class publicity including, but not limited to 
\duty
coordinating all advertising copy
\duty
providing and distributing posters advertising each class
\duty
organizing other special projects to advertise club and class activities
\duty
with the Secretary, writing and distributing a newsletter to club
members regularly.

\section
The Class Coordinator shall report to the President.  The
Class Assistants shall report to the Class Coordinator.
The Class Coordinator and Class Assistants shall
\duty
coordinate the class
\duty
take admission from class members
\duty
handle, with the Treasurer, the finances of the class
\duty
take attendance of class members
\duty
maintain and display a list of calls taught to the class
\duty
act as liaison between the club and the class
\duty
take requests for and place orders for club badges, with the
assistance of the Treasurer.

\section
The Booking Director shall 
\duty
book and sign contracts with callers and cuers for monthly dances
\duty
confirm arrangements with the caller and cuer shortly before each monthly dance 
\duty
report to the President.

\section
The Rooming Director shall
\duty
reserve rooms for club dances and other club functions
\duty
report to the President.

\section
The Banner Raids Director shall
\duty
organize banner raids and other visits to/from other square dance clubs
\duty
report to the President.

\section
The Archivist/Historian shall
\duty
maintain all club records except as otherwise governed by the
Constitution or the Bylaws
\duty
keep and maintain an up-to-date copy of the Constitution and the Bylaws
\duty
maintain a list of standing club policies
\duty
develop and maintain an accurate history of the club
\duty
report to the President.

\section
The Members-at-Large shall become as involved as possible in club affairs.

\section
Officers may exchange duties among themselves and their assistants as
they see fit.  An officer who will be unable to perform a duty may
assign that duty for a period of no more than four weeks to a
non-officer to be supervised by the Executive Committee.

\section
All officers and assistants may choose temporary helpers to assist
them in executing their duties.  A helper must be under the
supervision of an officer or assistant who has responsibility for that
task.  The helper is assigned for a specific task and has no other
club duties or responsibilities.

\article{The Executive Committee}
\section
Meetings of the Executive Committee shall be open to anyone who is
entitled to attend club meetings.
\section
Meetings of the Executive Committee shall be announced to the entire club when possible.
\section
Members of the Executive Committee shall be given
at least twenty-four hours' notice of all meetings of the Executive
Committee.
\section
The decisions of the Executive Committee are binding on all members of
the Executive Committee.
\section
Any expenditure over \$200 must have the prior approval of the club at
a club meeting.  The expenditure must be on the club meeting agenda.
\section
Appointed officers may be removed in the same way in which they were appointed.
\section
The Executive Committee may change an officership
to a committee for the duration of the current term of office.  The
current officer will become the committee coordinator and have all
current responsibilities.  New committee members must be approved by
the Executive Committee.
Executive Committee may also reduce a committee to an officership for
the duration of the current term of office. The current committee
coordinator will become the officer and have all current
responsibilities.
These changes do not affect the distribution of votes on the Executive
Committee.
\section
Temporary committees may be created by the Executive Committee or the
club as needed.
\section
Any appointed position (officer or committee
member) may remain unfilled.  The Executive Committee is responsible
for executing or delegating the duties of the unfilled position until
the position is filled.

\article{Meetings}
\section
Club meetings may not be held during monthly dances.
\section
Non-specific proxies shall not be allowed at club meetings.
\section
Members of the club shall be given at least two weeks' notice of
club meetings.

\article{Dances}
\section
The club level is the Callerlab Plus program.
\section
The general format of dances of the club shall be two square dances
alternating with two round dances, at the discretion of the Dance
Supervisor, caller and cuer.
\section
The Executive Committee may vote on free admission to club functions
for any club member.  Any such vote must be formally announced to the
club and shall expire with the term of that Executive Committee.

\article{Club Employees}
\section
{\it Club employee\/}
shall be defined as anyone who is paid for services rendered to the club.

\article{The Class}
\section
Except at the discretion of the Executive Committee, the class shall
be 14 weeks, preceded by at most two free nights.
\section
A class member must attend 80\%
of the class to graduate, except at the discretion of the
Executive Committee. 
\section
The club caller shall be responsible for teaching the class.
\section
The club may hold other workshops as appropriate.

\article{Elections}
\section
The term of office for officers elected in the spring shall begin on
the earlier of one week after the spring class graduation or June 1.
The term of office for officers elected in the fall, if any, shall
begin on the earlier of one week after the fall class graduation or
January~1.  Elections shall be held as close as is practical to two
months prior to the inception of office.
Fall elections, if any, shall be held only for the positions vacated
by elected officers who have chosen not to continue in office.
A majority of the votes cast by the voting
members present shall be required to elect any of the officers.

\section
Any person who has been a voting member of the club for at least the
past three months shall be eligible for election to any office except
that of President.  To be nominated for the office of President, a
candidate must have been a voting member of Tech Squares for at least
the past 10 months.  This section may be suspended temporarily
at a club meeting by a two-thirds vote of those present and voting.
Advance notice is not required.

\section
At the time of the elections, the newly-elected President shall appoint a
successor from among the other newly-elected officers to
assume the responsibilities of the Presidency should a vacancy occur.

\section
The new Executive Committee shall appoint officers as soon as possible
after the annual club elections.

\section
If a vacancy occurs in an elected office other than that of President,
the President shall appoint someone to fill the vacancy
temporarily.  A special club meeting shall be called to elect an
interim officer within four weeks of the vacancy unless MIT is in
summer session, in which case the election shall be held four weeks
after the start of the MIT fall term.

\section
If a vacancy occurs in the office
of the President, the successor shall assume the office until the
second club dance following, when a special election shall be held for
the remaining portion of the term of President.  If the office is
filled by any of the existing elected officers, an election shall be
held immediately for the remainder of the term of that officer, and so
on in succession.  After this election any non-affected officers
or committee members shall resume the office and duties they held prior
to the vacancy in the office of the President.

\article{Amendment}
\section
The Bylaws may be amended by a majority of the votes cast by the
voting members present at a club meeting.
\section
A proposed amendment to the Bylaws must be submitted in writing to the
Secretary.  The Secretary shall distribute copies of the proposed
amendment to the club at least four weeks before the club meeting at
which the vote on the amendment will be held.

\article{Ratification}
\section
These Bylaws shall be ratified when approved by a two-thirds vote of
those club members voting.  A provision for absentee ballots shall be
made.  At least four weeks' notice shall be given of the club meeting
at which the vote on the ratification shall be held.

\end{document}
